\documentclass[oneside,12pt]{article}
\usepackage{fontspec}
\usepackage{lmodern}
%\setmainfont{cmr12}
\defaultfontfeatures{Ligatures=TeX} % To support LaTeX quoting style
\usepackage{amsmath}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage{pstricks}
\usepackage{steinmetz}

\widowpenalty=1000
\clubpenalty=1000


\title{EL2425 - Slip Control \\ Meeting agenda 2016-11-16}
%\date{}

\begin{document}
\maketitle

\section{Done}

\begin{itemize}
  \item Installation of the optimization library in python needed for MPC.
    However, there are issues with the statement of the problem in terms of the
    language itself. This stating ``does not conform to DCP rules".

    \item Three packages are theoretically solved. PID Centerline,
      MPC centerline, MPC circular. Not tested in the reality due to the
      above mentioned issue.

    \item A new time-Constant has been updated as $1.3452$s. The experimental
      method and results are detailed hereafter.
\end{itemize}



\section{Ongoing}

  \subsection{Tracking the centerline of a lane using a PID controller}

    \input{./sections/theory_centerline_pid.tex}

  \subsection{Tracking the centerline of a lane using a MPC controller}

    \input{./sections/theory_centerline_mpc.tex}


  \subsection{Tracking the circumference of a circle using a MPC controller}

    \subsubsection{Theory}
      \input{./sections/theory_circular_mpc.tex}
    \subsubsection{Simulation}
      \input{./sections/simulation_circular_mpc.tex}

		\subsubsection{Model Validation}

		In order to create datasets to be compared against the simulations the
    following experiment has been done:\\
	  Feed the real car with a set of different inputs (in open loop,i.e. without
    controller) to recreate the expected behaviour. The recorded trajectory
    from Mocap will be used to run offline experiments.



		 \subsubsection{Time constant test}

		 With assumption that the car’s dynamic is a 1st-order system, we drive the
     car in straight line along the Y axis(global) as far as possible with speed of
     14 \%, 16 \%, 18\% and 20 \% respectively.
     It is hard to reach the static situation since the space is limited, that is, the
     data only describe the beginning part of the step response. One way to solve
     the problem is using the Identification Toolbox in Matlab, which is capable of
     “constructing mathematical models of dynamic systems from measured input-
     output data”.
     The τ value is 1.3452 by average.

\section{Issues}

\begin{itemize}
  \item There might be an issue regarding the execution time of the optimization
    algorithm on the vehicle.
  \item As mentioned Python library for optimization is not working properly.
    This will have to be solved either by trying to fix the problems or by
    using an alternative package to handle the optimization problems. More
    documentation to be provided.
\end{itemize}


\section{To do}

\begin{itemize}
  \item Measure sampling time from Mocap. It is accounted as the difference
    between two time stamps. In order to read and deliver this data a new field
    in the message that sends pose and orientation has to be created. Some
    difficulties with ROS have to be overcome.

  \item centerline pid testing postponed due to lidar ethernet adapter outage.
    Although it is reported to be fixed, the current ongoing tasks were not
    interrupted for the purpose.

  \item Emergency stop. Already implemented in provided code but does not
    always work.

  \item Prototyping of dynamic model in matlab.

  \item Project Review 1. During next team meeting the updated review will
    be discussed.

\end{itemize}


\section{Misc.}

The progress of the project can be observed in \texttt{trello} and \texttt{github}:

\begin{itemize}
  \item \url{https://trello.com/b/uEP0jl0B/slip-control}
  \item \url{https://gits-15.sys.kth.se/alefil/HT16_P2_EL2425}
  \item \url{https://gits-15.sys.kth.se/alefil/HT16_P2_EL2425_resources}
\end{itemize}


\end{document}
